The impacts of park access on health outcomes: a spatial comprehensive approach

### 2018-12-13 manuscript.Rnw
Add estimated models to document

\begin{table*}[ht]
  \caption{Commonly cited benefits of parks and greenspaces}
  \label{tab:parkbenefits}
\begin{tabular}{lp{11cm}}
  \hline
Category & Summary of Benefits\\
\hline
Physical Health & Provide clean drinking water \citep{Benedict2006}\\
 & Foster increased physical activity\\
 & Promote faster healing in hospitals \citep{Akbari2001}\\
 & Reduce of heat-related mortality \\
 & Reduce incidence of cardiovascular-related mortality \\
 & Improved air quality and related reductions in respiratory-related mortality \citep{Lovasi2008}\\
 & Reduce incidence of childhood asthma \citep{Wolf2008}\\
 & Improve birth outcomes\\
\hline
Mental Health & Reduce stress and mental fatigue\\
  & Reduce aggression\\
  & Enhance emotional and cognitive development\\
  & Improve behavioral outcomes in youth \\
\hline
Social Health & Enhanced community aesthetics\\
 & Reduce crime\\
 & Increase social interaction \\
\hline
Economic Health & Provide of ecosystem services\\
 & Increase residential property values and municipal property tax revenues\\
 & Attract more shoppers and increase economic activity to commercial districts \\
\hline
\end{tabular}
\end{table*}

@@

<<weights>>=
tracts.dnn <- dnearneigh(gCentroid(tracts, byid = TRUE), 0, 1.8 * 5280)
dists <- nbdists(tracts.dnn, gCentroid(tracts, byid = TRUE))
dists.inv <- lapply(dists, function(x) 1 / x)
W <- nb2listw(neighbours = tracts.dnn, glist = dists.inv,
              zero.policy = TRUE, style = "W")
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
@

@@

<<distances, warning=FALSE>>=
# calculate centroids of tracts and parks
pop_weighted_centroids <- read_csv("data/CenPop2010_Mean_TR36.csv") %>%
  mutate(geoid = str_c(STATEFP, COUNTYFP, TRACTCE))
pop_weighted_centroids <- left_join(tracts@data, pop_weighted_centroids, by = "geoid") %>%
  dplyr::select(geoid, LONGITUDE, LATITUDE) %>%
  st_as_sf(crs = 4326, coords = c("LONGITUDE", "LATITUDE")) %>%
  st_transform(2263) 
parks <- parks %>% st_transform(st_crs(pop_weighted_centroids))

@@

<<logsum_betas>>=
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(log(distances), parks$log_size,
                                       betas = c(-0.42, 1.0)),
    tweets_ls = calculate_park_logsums(log(distances), parks$log_size, parks$log_tweets,
                                       betas = c(-0.42, 1.0)),
    distance_ls = (distance_ls - mean(distance_ls) )/ sd(distance_ls),
    access_ls = (access_ls - mean(access_ls) )/ sd(access_ls),
    tweets_ls = (tweets_ls - mean(tweets_ls) )/ sd(tweets_ls)
  )

@@

<<leaflet, eval=FALSE>>=
# this interactive map is much easier to create and explore
pal <- colorQuantile("Spectral", tracts_sf$access_ls, n = 5)
leaflet(tracts_sf) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(group = "access", color = ~ pal(access_ls), label = ~as.character(round(access_ls,2))) 
@

@@

<<map>>=
map <- ggmap(get_map(unname(st_bbox(tracts_sf)), source = "stamen", maptype = "toner"),
             extent = "device")
map +
  geom_sf(data = tracts_sf, inherit.aes=FALSE, 
          aes(fill = cut(access_ls, quantile(access_ls))), alpha = 0.8) +
  scale_fill_brewer("Relative Park Logsum", palette = "GnBu")
@
  \caption{Relative surplus-based accessibility in New York City}
  \label{fig:map}
\end{figure*}

@@

```{r spatial selection}
obese_base_lm <- lm(update(base_formula, log_obesity ~ .), data = tracts@data)
obese_base_sar <- lagsarlm(update(base_formula, log_obesity ~ .), 
                           data = tracts@data, listw = W, zero.policy = TRUE)
obese_base_sem <- errorsarlm(update(base_formula, log_obesity ~ .), 
                             data = tracts@data, listw = W, zero.policy = TRUE)
obese_base_sdm <- lagsarlm(update(base_formula, log_obesity ~ .), 
                           data = tracts@data, listw = W, zero.policy = TRUE, 
                           type = "mixed")
```

@@

```{r lrtest}
lmtest::lrtest(obese_base_sem, obese_base_sdm)
```

```{r obesity_access_models}
access_sdm <- update(obese_base_sdm, .~ . + access_ls)
tweets_sdm <- update(obese_base_sdm, .~ . + tweets_ls)
```

>>>>

\begin{table*}[ht]
  \caption{Commonly cited benefits of parks and greenspaces}
  \label{tab:parkbenefits}
\begin{tabular}{lp{11cm}}
\toprule
Category & Summary of Benefits\\
\midrule
Physical Health & Provide clean drinking water \citep{Benedict2006}\\
 & Foster increased physical activity\\
 & Promote faster healing in hospitals \citep{Akbari2001}\\
 & Reduce of heat-related mortality \\
 & Reduce incidence of cardiovascular-related mortality \\
 & Improved air quality and related reductions in respiratory-related mortality \citep{Lovasi2008}\\
 & Reduce incidence of childhood asthma \citep{Wolf2008}\\
 & Improve birth outcomes\\
\midrule
Mental Health & Reduce stress and mental fatigue\\
  & Reduce aggression\\
  & Enhance emotional and cognitive development\\
  & Improve behavioral outcomes in youth \\
\midrule
Social Health & Enhanced community aesthetics\\
 & Reduce crime\\
 & Increase social interaction \\
\midrule
Economic Health & Provide of ecosystem services\\
 & Increase residential property values and municipal property tax revenues\\
 & Attract more shoppers and increase economic activity to commercial districts \\
\bottomrule
\end{tabular}
\end{table*}

@@

<<weights>>=
pop_weighted_centroids <- read_csv("data/CenPop2010_Mean_TR36.csv") %>%
  mutate(geoid = str_c(STATEFP, COUNTYFP, TRACTCE))
pop_weighted_centroids <- left_join(tracts@data, pop_weighted_centroids, by = "geoid") %>%
  dplyr::select(geoid, LONGITUDE, LATITUDE) %>%
  st_as_sf(crs = 4326, coords = c("LONGITUDE", "LATITUDE")) %>%
  st_transform(2263)

tracts.dnn <- dnearneigh(gCentroid(as(pop_weighted_centroids, "Spatial"), byid = TRUE), 
                         0, 1.8 * 5280)
dists <- nbdists(tracts.dnn, gCentroid(tracts, byid = TRUE))
dists.inv <- lapply(dists, function(x) 1 / x)
W <- nb2listw(neighbours = tracts.dnn, glist = dists.inv,
              zero.policy = TRUE, style = "W")
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
@

@@

<<distances, warning=FALSE>>=
# calculate centroids of tracts and parks

parks <- parks %>% st_transform(st_crs(pop_weighted_centroids))

@@

<<logsum_betas>>=
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(log(distances), parks$log_size,
                                       betas = c(-0.42, 1.0)),
    tweets_ls = calculate_park_logsums(log(distances), parks$log_size, parks$log_tweets,
                                       betas = c(-0.42, 1.0, 0.1)),
    access_ls = (access_ls - mean(access_ls) )/ sd(access_ls),
    tweets_ls = (tweets_ls - mean(tweets_ls) )/ sd(tweets_ls)
  )

@@

<<leaflet, eval=FALSE>>=
# this interactive map is much easier to create and explore
pal <- colorQuantile("Spectral", tracts_sf$access_ls, n = 5)
leaflet(tracts_sf) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(group = "access", color = ~ pal(access_ls), 
              label = ~as.character(round(access_ls,2))) %>% 
  addPolygons(group = "tweets", color = ~ pal(tweets_ls), 
              label = ~as.character(round(tweets_ls,2))) %>%
  addLayersControl(baseGroups = c("access", "tweets"))
@

@@

<<map, echo=FALSE, message=FALSE, warning=FALSE>>=
library(ggmap)
map <- ggmap(get_map(unname(st_bbox(tracts_sf)), source = "stamen", maptype = "toner"),
             extent = "device")
map +
  geom_sf(data = tracts_sf, inherit.aes=FALSE, 
          aes(fill = cut(access_ls, quantile(access_ls))), alpha = 0.8) +
  scale_fill_brewer("Relative Park Logsum", palette = "GnBu")
@
  \caption{Relative surplus-based accessibility in New York City}
  \label{fig:map}
\end{figure*}

@@

<<spatial selection>>=
obese_base_sem <- errorsarlm(update(base_formula, log_obesity ~ .), 
                             data = tracts@data, listw = W, zero.policy = TRUE)
obese_base_sdm <- lagsarlm(update(base_formula, log_obesity ~ .), 
                           data = tracts@data, listw = W, zero.policy = TRUE, 
                           type = "mixed")
test_sdmsem <- lmtest::lrtest(obese_base_sem, obese_base_sdm)
@

@@

<<access_sdm>>=
# estimate models
access_sdm <- update(obese_base_sdm, .~ . + access_ls)
tweets_sdm <- update(obese_base_sdm, .~ . + tweets_ls)
@

\begin{table*}
  \caption{Estimated Coefficients on Obesity}
  \label{fig:obeseity_models}
<<modelchart, results="asis">>=
library(texreg)
obesity_models <- list(Base = obese_base_sdm, `Access` = access_sdm, 
                       `Access + Tweets` = tweets_sdm)
texreg(obesity_models, digits = 4, table = FALSE, single.row = TRUE, 
       booktabs = TRUE, use.packages = FALSE)
@
\end{table*}
